---
title: "VAR modeling"
author: "An Tran"
date: "9/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(vars)
library(astsa)
library(forecast)
library(readxl)
library(xts)
require(graphics)
```


```{r}
us_macro <- read_excel("Data_external.xlsx")
us_yields <- read_excel("Data_interest rate_all terms.xlsx")
m = cbind(us_macro,us_yields)

View(list(us_yields,us_macro))
View(list(m$unrate,m$gdp))
View(m$unrate)
```


```{r}
colnames(m) <- c("DATE", "mth1", "mth3", "mth12", "mth36", "mth60","gdp","unrate", "inf")
plot.ts(m$unr,y=NULL,plot.type = "multiple","single", axes = TRUE)
```


#compute the GDP growth rate with two methods --> the same output but not yet
```{r}
#gdp_growth <- xts(1200 * log(gdp/stats::lag(gdp,1)))
#gdp_growth1 <- ts(1200*log(gdp[-1]/gdp[-length(gdp)]))
#View(list(gdp_growth,gdp_growth1))
```

#Error when combine the "un" variable
```{r}
#x11 = cbind(mth3,un)
#var2 <- VAR(x1, p=2, type = "const")
#summary(var2)
```


```{r}
x1 = cbind(mth3,gdp)
var2 <- VAR(x1, p=2, type = "const")
summary(var2)
```


# Test serial correlation using Portmanteau test
we test that the residuals are uncorrelated
H0: Null hypothesis of no autocorrelation
Ha: Autocorrelation 
Reject: p-value << 0.05
reject --> Ho, accept
```{r}
serial.test(var2, lags.pt = 10, type = "PT.asymptotic")
```


# Augmented Dickey-Fuller Test Unit Root (ADF)

To find if a series has a unit root 
a series with a trend-line -> non-stationary -> will have a unit root

check for a unit root, where we note that we able to reject null of unit root when using the Dickey-Fuller test.

H0: random walk
Ha: trend/stationary process

```{r}
adf.mth3<- ur.df(mth3, type = "trend", selectlags = "AIC")
summary(adf.mth3)
```

```{r}
info <- VARselect(x1, lag.max = 24, type = "const")
info$selection
```


```{r}
serial <- serial.test(var2, lags.pt = 10, type = "PT.asymptotic")
plot(serial, names = "mth3")
```

# multivariate ARCH Lagrange-Multiplier test
Heteroscedasticity in the residuals 
p-value that is greater than 5% would indicate the absence of heteroscedasticity

H0: Research H0: heteroscedasticity 
Ha: the absence of heteroscedasticity
=> non-heteroscedasticity
```{r}
arch <- arch.test(var2, lags.multi = 12, multivariate.only = TRUE)
arch
```

# Normality test
distribution of the residuals
Big p-value: not normally distributed

H0: normally distributed
Ha: not normally distributed
```{r}
norm <- normality.test(var2, multivariate.only = TRUE)
norm
```


# Granger causality
```{r}
mth3.cause <- causality(var2, cause = "mth3")
mth3.cause
```


#Error when adding the "un" variable
```{r}
# Model 3: Use only 3 variables and 2 lags
x2 = cbind(mth3,gdp,inf)
var2 <- VAR(x2, p=2, type = "const")
summary(var2)
```


```{r}
# Model 3: Use only 3 variables and 2 lags
x2 = cbind(mth3,gdp,inf)
var2 <- VAR(x2, p=2, type = "const")
summary(var2)
```

View and analyze residuals of mth3 equation

```{r}
acf(residuals(var2)[,2])
```

# HYPOTHESIS
# testing independence (serial correlation)
Ljung-Box test for independence
a non-stationary signal will have a low p-value
a stationary (white noise/random) will have high p-value

H0: independent
H1: non-independent
-> non-stationary,wanna stationary
```{r}
#lag.length = 26
Box.test(inf, lag = 26, type = "Ljung-Box")
Box.test(un, lag = 26, type = "Ljung-Box")
```

# Augmented Dickey–Fuller (ADF) test for unit root

To find if a series has a unit root 
a series with a trendline -> nonstationary -> will have a unit root

```{r}
options(warn=-1)
library(tseries)
```

```{r}
adf.test(inf)
adf.test(gdp)
adf.test(mth3)
#Ho: non-stationary,
#H1: stationary
```

H0: non-stationary (series has a unit root)
H1: stationary (white noise/random)


#Kwiatkowski-Phillips-Schmidt-Shin (KPSS)

```{r}
#remove use ADF
kpss.test(gdp, null = "Trend")
kpss.test(inf, null = "Trend")
kpss.test(mth3, null = "Trend")
```

---
title: NEW CODE
Cite: Day7-OOS
---

#Forecast using VAR, with h = how many periods into the future
#Error, cant fix yet
```{r}
fc <- forecast(var2, h = 1)
plot(fc)
print(fc)
```
#time series object = matrix

#Error
```{r}
# First example in reporting OOS performance 
# 1. Split your data into train/test
training <- window(x1, end = 2010)
test <- window(x1, start = 2015)
````


```{r}
# 2. Fit my model on training

fit <- VAR(training, p = 10, type = "const")

# 3. Predict on test set

fcast <- forecast(fit, h = 40)

actual_y <- as.data.frame(test[,1])
predicted_y_hat <- as.data.frame(fcast$forecast$mth3$mean)

# 4. Compute RMSE
result <- cbind(actual_y, predicted_y_hat)
names(result) <- c("Actual", "Predicted")
result$sq_err <- (as.numeric(result$Actual) - as.numeric(result$Predicted))^2
RMSE <- sqrt(mean(result$sq_err))
````




























